### 2021-11-30 documentos/generators.tex
Comments on corrections added

\cpnote{Mucha lora y no se prueba nada}
PCE generators $\pceg$ obey a symmetry
that defines uniquely every PCE generator. The coefficients  $\{\taus\}$ of every 
generator $\pceg$ arranged in a hypercubic $N$-dimensional array 
%of dimensions $\underbrace{4\times 4\times\ldots\times 4}_{N}$ 
obey a symmetry with respect to the $N$ hyperplanes of dimension $N-1$
\janote{según wikipedia, por definición, los hiperplanos son de dimensión 
$N-1$. Así que podría quitarse la aclaración de la dimensión. Lo dejo así y 
espero retroalimentación} 
that separate the array into two half arrays \janote{No estoy tan satisfecho con la redacción de este enunciado}.
See, in \Fref{fig:examplesPCE}, that generators $\mcG_{(1,3)}$, $\mcG_{(3,2)}$
and $\mcG_{(2,2)}$ represented in (c), (d) and (e), respectively,
are either symmetric or anti-symmetric with respect to the lines that cut vertically 
and horizontally in half the diagrams. In fact, this symmetry may be used to
construct all generators $\pceg$ as follows. Start out with $\tau_{0,\ldots,0}=1$
and begin to ``unfold'' the array of all $\pceg$'s coefficients $\taus$ by deciding
whether $\tau_{0,\ldots,0,1}$ be set to 1 or 0 (symmetric or anty-simmetric with 
respect to $\tau_{0,\ldots,0}$), then choose the values of $\{\tau_{0,\ldots,0,2}, 
\tau_{0,\ldots,0,3}\}$ to be symmetric or anti-symmetric with respect to 
$\{\tau_{0,\ldots,0},\tau_{0,\ldots,0,1}\}$; you need to keep this procedure 
for the remaining subsets with $2l$ coefficients $\taus$, with $l$ the cardinality of 
the previous subset, by setting the coefficients $\taus=0,1$ in order to be symmetric or
anti-symmetric to the previous subset. For example, let us illustrate the 
procedure to construct $\mcG_{(3,2)}$ represented in \Fref{fig:examplesPCE}(d).
One starts out choosing the value of $\tau_{(0,1)}$ to be anti-symmetric to $\tau_{(0,0)}$, then one chooses 
$\qty{\tau_{(0,2)},\tau_{(0,3)}}$ symmetric to $\qty{\tau_{(0,0)},\tau_{(0,1)}}$,
$\qty{\tau_{(1,0)},\tau_{(1,1)},\tau_{(1,2)},\tau_{(1,3)}}$ anti-symmetric 
to $\qty{\tau_{(0,0)},\tau_{(0,1)},\tau_{(0,2)},\tau_{(0,3)}}$, and finally
the last eight components $\tau_{\vec\alpha}$ anti-symmetric to the first 
eight.

@@

\cpnote{Mucha lora y no se prueba nada, again}
The matrix $\san$ [see \eref{eq:san}] encodes all the information
of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
The rows and columns of matrix $A$ also obey the symmetry previously discussed 
for PCE generators $\pceg$. It suffices to check that rows and columns of matrix $a$
in \Eref{eq:1} obey the aforementioned symmetry when they are arranged in a hypercubic 
$N$-dimensional array of order $4$.
As a consequence of $a$'s elements being $\pm1$, the power tensor $a^{\otimes N}$ will hold the symmetry of the 
rows and columns of $A$. 
Therefore, this establishes a deep connection between the matrix $A$ and 
PCE quantum channels. It allows one to infer the PCE generators $\pceg$
by taking its corresponding coefficients $\{\taus\}$ as the rows or columns of $A$ 
after taking $-1\mapsto0$. In \appref{sec:2_qubits} we illustrate this program 
for 2-qubits PCE channels.
In short, it is sufficient to have the matrix $A$ to construct 
all PCE quantum channels.
%\janote{Aquí
%tendrá que ir una prueba que aún se está cocinando}

>>>>

\cpnote{Mucha lora y no se prueba nada}
PCE generators $\pceg$ obey a symmetry
that defines uniquely every PCE generator. The coefficients  $\{\taus\}$ of every 
generator $\pceg$ arranged in a hypercubic $N$-dimensional array 
%of dimensions $\underbrace{4\times 4\times\ldots\times 4}_{N}$ 
obey a symmetry with respect to the $N$ hyperplanes of dimension $N-1$
\janote{según wikipedia, por definición, los hiperplanos son de dimensión 
$N-1$. Así que podría quitarse la aclaración de la dimensión. Lo dejo así y 
espero retroalimentación} 
that separate the array into two half arrays \janote{No estoy tan satisfecho con la redacción de este enunciado}.
See, in \Fref{fig:examplesPCE}, that generators $\mcG_{(1,3)}$, $\mcG_{(3,2)}$
and $\mcG_{(2,2)}$ represented in (c), (d) and (e), respectively,
are either symmetric or anti-symmetric with respect to the lines that cut vertically 
and horizontally in half the diagrams. In fact, this symmetry may be used to
construct all generators $\pceg$ as follows.\janote{sintetizar} Start out with $\tau_{0,\ldots,0}=1$
and begin to ``unfold'' the array of all $\pceg$'s coefficients $\taus$ by deciding
whether $\tau_{0,\ldots,0,1}$ be set to 1 or 0 (symmetric or anty-simmetric with 
respect to $\tau_{0,\ldots,0}$), then choose the values of $\{\tau_{0,\ldots,0,2}, 
\tau_{0,\ldots,0,3}\}$ to be symmetric or anti-symmetric with respect to 
$\{\tau_{0,\ldots,0},\tau_{0,\ldots,0,1}\}$; you need to keep this procedure 
for the remaining subsets with $2l$ coefficients $\taus$, with $l$ the cardinality of 
the previous subset, by setting the coefficients $\taus=0,1$ in order to be symmetric or
anti-symmetric to the previous subset. For example, let us illustrate the 
procedure to construct $\mcG_{(3,2)}$ represented in \Fref{fig:examplesPCE}(d).
One starts out choosing the value of $\tau_{(0,1)}$ to be anti-symmetric to $\tau_{(0,0)}$, then one chooses 
$\qty{\tau_{(0,2)},\tau_{(0,3)}}$ symmetric to $\qty{\tau_{(0,0)},\tau_{(0,1)}}$,
$\qty{\tau_{(1,0)},\tau_{(1,1)},\tau_{(1,2)},\tau_{(1,3)}}$ anti-symmetric 
to $\qty{\tau_{(0,0)},\tau_{(0,1)},\tau_{(0,2)},\tau_{(0,3)}}$, and finally
the last eight components $\tau_{\vec\alpha}$ anti-symmetric to the first 
eight.

@@

\cpnote{Mucha lora y no se prueba nada, again}
The matrix $\san$ (and thus $a$) [see \eref{eq:san}] encodes all the information
of PCE generators $\pceg$ and, therefore, of all PCE quantum channels. 
The rows and columns of matrix $A$ also obey the symmetry previously discussed 
for PCE generators $\pceg$. It suffices to check that rows and columns of matrix $a$
in \Eref{eq:1} obey the aforementioned symmetry when they are arranged in a hypercubic 
$N$-dimensional array of order $4$.
As a consequence of $a$'s elements being $\pm1$, the power tensor $a^{\otimes N}$ will hold the symmetry of the 
rows and columns of $A$. \janote{falta prueba}
Therefore, this establishes a deep connection between the matrix $A$ and 
PCE quantum channels. It allows one to infer the PCE generators $\pceg$
by taking its corresponding coefficients $\{\taus\}$ as the rows or columns of $A$ 
after taking $-1\mapsto0$. In \appref{sec:2_qubits} we illustrate this program 
for 2-qubits PCE channels.
In short, it is sufficient to have the matrix $A$ to construct 
all PCE quantum channels.
%\janote{Aquí
%tendrá que ir una prueba que aún se está cocinando}
